How fluid-mechanical erosion creates anisotropic porous media

### 2022-06-14 docs/PhysicsPaper/StokesErosion.tex
NM

% dematerialize, disintegrate
%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%

@@

The effects of flow-induced erosion are visible across a range of scales in the natural world, from massive geological structures, to mesoscopic patterns, and down to the  granular constituents that comprise a porous medium.

% ORIGINAL BELOW
Effects of flow-induced erosion are visible across a range of scales, from massive geological structures, to mesoscopic patterns, and down to the tiny granular constituents that comprise a porous medium. In the case of a porous medium specifically, it has been long recognized that bulk properties of mediums encountered in nature are typically anisotropic, so that the medium allows flow in a preferred direction more easily. This anisotropy is commonly attributed to how grains are deposited, with their longest dimension parallel to the settling bed, so that they allow flow preferentially in the horizontal direction. Controlled experiments, however, have not been performed to test this hypothesis. Here, we use highly-accurate numerical simulations to examine an alternative, and possibly complementary, mechanism: namely, that the flow-induced erosion of the medium's solid constituents contributes to its overall anisotropy.

@@

With both the longitudinal and transverse components of permeability calculated, we define the anisotropy of the medium as the ratio
\begin{equation}
\anis = k_{11} / k_{22}
\end{equation}
Note that the random configuration of circles used to initialize the erosion simulations will have an anisotropy nearly equal to one, and as the configuration erodes, the configuration would be expected to permit flow in the longitudinal direction more easily than in the transverse direction, yielding $\anis > 1$.

@@

It is possible to device a test to isolate these two types of anisotropy.
Introduce circular bodies with same centers of mass...
Thus, the configurational anisotropy is defined as
\begin{equation}
\anis_C = k_1^{(c)} / k_2^{(c)}
\end{equation}

>>>>

% dematerialize, disintegrate
% internal, permeating, intervening
%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%

@@

The effects of flow-induced erosion are visible across a range of scales in the natural world, from massive geological structures \cite{abrams2009growth, perkins2015amplification, mac2020ultra, sharma2022alcove, mac2022morphological}, to mesoscopic patterns \cite{berhanu2012shape, bertagni2021hydrodynamic}, and down to the granular constituents comprising porous media \cite{zareei2022temporal}. Porous media encountered in natural settings typically exhibit {\em anisotropic} material properties,

\vsp{5}
% ORIGINAL BELOW
Effects of flow-induced erosion are visible across a range of scales, from massive geological structures, to mesoscopic patterns, and down to the tiny granular constituents that comprise a porous medium. 
In the case of a porous medium specifically, it has been long recognized that bulk properties of mediums encountered in nature are typically anisotropic, so that the medium allows flow in a preferred direction more easily. 
This anisotropy is commonly attributed to how grains are deposited, with their longest dimension parallel to the settling bed, so that they allow flow preferentially in the horizontal direction. Controlled experiments, however, have not been performed to test this hypothesis. Here, we use highly-accurate numerical simulations to examine an alternative, and possibly complementary, mechanism: namely, that the flow-induced erosion of the medium's solid constituents contributes to its overall anisotropy.

@@

With both the longitudinal and transverse components of permeability calculated, we define the anisotropy of the medium as the ratio
\begin{equation}
\anis = k_{11} / k_{22}
\end{equation}
Note that the random configuration of circles used to initialize the erosion simulations will have an anisotropy nearly equal to one. As this configuration erodes, it would be expected to permit flow in the longitudinal direction more easily than in the transverse direction, yielding $\anis > 1$.

@@

It is possible to devise a test to isolate these two types of anisotropy.
Introduce circular bodies with same centers of mass...
Thus, the configurational anisotropy is defined as
\begin{equation}
\anis_C = k_1^{(c)} / k_2^{(c)}
\end{equation}
